Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2018-07-25 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd
Minor bug fix

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 folderName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)')
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## It is assumed your working directory is where this file

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
parentId = 'syn9846623';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (DLPFC)';

@@

# Code
CODE <- synapseClient::Folder("HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)", 
                              parentId = parentId)
synapseClient::synSetAnnotations(CODE, annotations = all.annotations)
CODE <- synapseClient::synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_ModSel.Rmd",
                                 parentId ="syn9846623",
                                 entityName = 'HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)')
```

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
## It is assumed your working directory is where this file

@@

```{r synapse.parameters, include=FALSE, cache=FALSE}
parentId = 'syn9846623';
activityName = 'Covariate adjustments';
activityDescription = 'Covariate analysis of STAR aligned feature counts with Ensembl v75 with CQN normalisation (DLPFC)';

@@

# Code
CODE <- synapseClient::Folder(name = "HBCC - DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN (Model Selection)", 
                              parentId = parentId)
synapseClient::annotations(CODE) = all.annotations
CODE <- synapseClient::synStore(CODE)
